### 2017-06-19 abstract1.tex
final

% \markboth{中~文~摘~要}{中~文~摘~要}
\begin{tabular}{l l}
论文题目：& 面向知识图谱溯因诊断的研究\\
专\quad\quad 业：& 软件工程\\
硕\,\,\,士\,\,\,生：& \\
指导教师：& \quad \\
\end{tabular}
\vspace{1cm}
%\chapter*{摘\quad 要}

@@

我们的目标是计算所有合理解释，合理的解释需要满足的条件包括可接受， 非平凡，一致并且是$\subseteq_\mathsf{ds}$-$\emph{minimal}$的。在本文中，我们提供了完整的算法来计算所有满足条件的解释。我们还利用生成的解释来实现对知识库的修复。我们基于本文提出的算法实现了PBA系统，在PBA系统中我们测试了决断集模版对知识库的诊断能力。实验结果证明了我们提出的方法具有有效性以及合理性。

>>>>

% \markboth{中~文~摘~要}{中~文~摘~要}
\begin{tabular}{l l}
论文题目：& 面向知识图谱溯因诊断的研究\\
专\quad\quad 业：& 软件工程\\
硕\,\,\,士\,\,\,生：& 马华冠\\
指导教师：& 万海\quad  副教授\\
\end{tabular}
\vspace{1cm}
%\chapter*{摘\quad 要}

@@

我们的目标是计算所有合理解释，合理的解释需要满足的条件包括可接受， 非平凡，一致并且是$\subseteq_\mathsf{ds}$-$\emph{minimal}$的。在本文中，我们提供了完整的算法来计算所有满足条件的解释。我们还利用生成的解释来实现对知识库的修复。我们基于本文提出的算法实现了PBA系统，在PBA系统中测试了基于决断集模板的诊断框架对知识库的诊断能力。实验结果证明了我们提出的方法具有有效性以及合理性。

### 2017-06-19 abstract2.tex
final

%\thispagestyle{empty} %取消当前页码
%\chapter[ABSTRACT（英文摘要）]{Abstract}
\begin{tabular}{l l}
Title：& Research on the Abduction of Knowledge Graph\\
Major：& Software Engineering\\
Name：& \\
Supervisor：& \\
\end{tabular}
\vspace{1cm}
%\chapter*{Abstract}
% \markboth{英~文~摘~要}{英~文~摘~要}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}

@@

Our goal is to calculate all reasonable explanations, reasonable explanations that need to be met, including acceptable, non-trivial, consistent and is $\subseteq_\mathsf{ds}$ - $\emph{minimal}$. In this paper, we provide a complete algorithm to compute all explanations that satisfy the condition. We also use the generated explanation to achieve the repair of the knowledge base. We have implemented the PBA system based on the algorithm proposed in this paper. In the PBA system, we have tested the ability to solve the knowledge base. The experimental results show that the proposed method is effective and reasonable.

>>>>

%\thispagestyle{empty} %取消当前页码
%\chapter[ABSTRACT（英文摘要）]{Abstract}
\begin{tabular}{l l}
Title：& Research on the Abductive Diagnosis of Knowledge Graph\\
Major：& Software Engineering\\
Name：& Huaguan Ma\\
Supervisor：& A/Prof. Hai Wan\\
\end{tabular}
\vspace{1cm}
%\chapter*{Abstract}
% \markboth{英~文~摘~要}{英~文~摘~要}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}

@@

Our goal is to calculate all reasonable explanations, reasonable explanations that need to be met, including acceptable, non-trivial, consistent and is $\subseteq_\mathsf{ds}$ - $\emph{minimal}$. In this paper, we provide a complete algorithm to compute all explanations that satisfy the condition. We also use the generated explanation to achieve the repair of the knowledge base. We have implemented the PBA system based on the algorithm proposed in this paper. In the PBA system, the diagnostic capability of the diagnostic framework based on the justification pattern is tested. The experimental results show that the proposed method is effective and reasonable.

### 2017-06-19 cover.tex
final

 \vspace{20mm}
 \begin{center}
 {\bfseries\song\fontsize{20pt}{\baselineskip}\selectfont
    稳定模型语义下不一致本体规则修复及回答查询的研究}\\
 \end{center}
 \begin{center}
 {\bfseries\fontsize{17pt}{\baselineskip}\selectfont
    Query Answering with Existential Rules Repairs of Inconsistent Ontologies under Stable Model Semantics}\\
 \end{center}

@@

 \>{\sanhao 学位申请人：} \> \underline{\sihao 肖\,鹏\hspace{4.07cm}}\\ %总长3.4cm
 \\
 \>{\sanhao 指\,\,导\,\,教\,\,师：} \> \underline{\sihao 万\,海\;\;高级讲师\hspace{1.88cm}}\\
 \\
 \>{\sanhao 专\,\,业\,\,名\,\,称：}\> \underline{\sihao 软件工程\hspace{3.2cm}}\\
 \end{tabbing}
\vspace{12mm}

@@

 \begin{center}\sanhao
 \;\;二零一五\,年\;五\,月
 \end{center}
 \newpage
 \normalsize
 \song

>>>>

 \vspace{20mm}
 \begin{center}
 {\bfseries\song\fontsize{20pt}{\baselineskip}\selectfont
    面向知识图谱溯因诊断的研究}\\
 \end{center}
 \begin{center}
 {\bfseries\fontsize{17pt}{\baselineskip}\selectfont
	Research on the Abduction of Knowledge Graph}\\
 \end{center}

@@

 \>{\sanhao 学位申请人：} \> \underline{\sihao \,\hspace{4.07cm}}\\ %总长3.4cm
 \\
 \>{\sanhao 指\,\,导\,\,教\,\,师：} \> \underline{\sihao \,\;\;\hspace{1.88cm}}\\
 \\
 \>{\sanhao 专\,\,业\,\,名\,\,称：}\> \underline{\sihao 软件工程\hspace{3.2cm}}\\
 \end{tabbing}
\vspace{12mm}

@@

 \begin{center}\sanhao
 \;\;二零一七\,年\;五\,月
 \end{center}
 \newpage
 \normalsize
 \song

### 2017-06-19 public.tex
...
final

\renewcommand{\labelenumi}{[\arabic{enumi}].}
\begin{enumerate}
\item 	Jianfeng Du, Hai Wan, \textbf{Huaguan Ma}. Practical TBox Abduction Based on Justification Patterns [C].//
Proceedings of the 31th AAAI Conference on Artificial
Intelligence (AAAI-17). 2017.
\end{enumerate}

>>>>

\renewcommand{\labelenumi}{[\arabic{enumi}].}
\begin{enumerate}
\item 	Jianfeng Du,Hai Wan,Huaguan Ma. Practical TBox Abduction Based on Justification Patterns//
Proceedings of the 31th AAAI Conference on Artificial
Intelligence (AAAI-17). 2017.

注：此论文的内容由本文第三、四章的工作扩展而来
\end{enumerate}
